### 2017-08-18 doc/msi-api.tex
fixing minor errors in User's Guide

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{API Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The MSI API's are provided in the file \texttt{``msi.h"}. Throughout this section, unless specified, DOF, matrix row and column ID's are specified by a local ID. A word ``\emph{global}" in a function name indicates that the function involves global operation or global data.

@@

\begin{tabular}{lp{14cm}}	
	pMesh
        pMeshEnt 
        pField & 	a field handle (defined in \texttt{``pumi.h"})\\
	pOwnership & 	a user-defined ownership handle (defined in \texttt{``pumi.h"}) \\
 	pMatrix &	a matrix handle \\
\end{tabular}

@@

In terms of field operation, MSI provides the field creation only as PUMI field creation routine, \texttt{pumi$\_$field$\_$create}, does not support \textit{multiple values}. For the rest of field operations including field deletion, use the API's in \texttt{PUMI.h}. If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.

@@

@@

\begin{verbatim}
void msi_matrix_multiply (
    pMatrix  /* in */  A, 
    pField  /* in */   x, 
    pField  /* out */  b)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle ($A$) of type 0 (\textit{MSI$\_$MULTIPLY}) and an input field handle ($x$), perform the matrix-vector multiplication \textit{``Ax"} and write the result in the field $b$. If the input matrix or the input field is complex-valued, the output field must be complex-valued.

\begin{verbatim}
void msi_matrix_solve (
        pMatrix  /* in */   A, 
        pField   /* in */   b, 
        pField   /* out */  x)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle ($A$) of type 1 (\textit{MSI$\_$SOLVE}) and a RHS field handle ($b$), solve the global discrete equation \textit{``Ax=b"} and write the solution into the field $x$.

@@

\begin{verbatim}
void msi_matrix_write (
    pMatrix  /* in */  matrix, 
    const char*  /* in */  file_name, 
    int  /* in */  start_index=0)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, file name and a starting local ID for nodes (default is 0), write the $non$-$zero$ matrix values in file(s). For each process \textit{i}, the matrix information is written in \texttt{``filename-i"}. If \textit{file$\_$name} is \textit{NULL}, \texttt{msi$\_$matrix$\_$print} is performed.
PUMI provides an equivalent API for fields and nodes.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{API Overview}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The MSI API's are provided in the file ``\texttt{msi.h}". Throughout this section, unless specified, DOF, matrix row and column ID's are specified by a local ID. A word ``\emph{global}" in a function name indicates that the function involves global operation or global data.

@@

\begin{tabular}{lp{14cm}}	
	pMesh  & 	a mesh instance (defined in ``\texttt{pumi.h}")\\
        pMeshEnt & 	a mesh entity handle (defined in ``\texttt{pumi.h}")\\
        pField & 	a field handle (defined in ``\texttt{pumi.h}")\\
	pOwnership & 	a user-defined ownership handle (defined in ``\texttt{pumi.h}") \\
 	pMatrix &	a matrix handle \\
\end{tabular}

@@

In terms of field operation, MSI provides the field creation only as PUMI field creation routine, \texttt{pumi$\_$field$\_$create}, does not support \textit{multiple values}. For the rest of field operations including field deletion, use the API's in \texttt{PUMI.h}.

@@

 If $nv$ is 1, \texttt{msi$\_$field$\_$create (m, field$\_$name, nv, nd)} is equivalent to \texttt{pumi$\_$field$\_$create (m, field$\_$name, nd)}.

@@

\begin{verbatim}
void msi_matrix_multiply (
    pMatrix  /* in */  A, 
    pField  /* in */   x, 
    pField  /* out */  b)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle ($A$) of type 0 (\textit{MSI$\_$MULTIPLY}) and an input field handle ($x$), perform the matrix-vector multiplication \textit{``Ax}" and write the result in the field $b$. If the input matrix or the input field is complex-valued, the output field must be complex-valued.

\begin{verbatim}
void msi_matrix_solve (
        pMatrix  /* in */   A, 
        pField   /* in */   b, 
        pField   /* out */  x)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle ($A$) of type 1 (\textit{MSI$\_$SOLVE}) and a RHS field handle ($b$), solve the global discrete equation \textit{``Ax=b}" and write the solution into the field $x$.

@@

\begin{verbatim}
void msi_matrix_write (
    pMatrix  /* in */  matrix, 
    const char*  /* in */  file_name, 
    int  /* in */  start_index=0)
\end{verbatim}\vspace{-.5cm}\hspace{1cm}
Given a matrix handle, file name and a starting local ID for nodes (default is 0), write the $non$-$zero$ matrix values in file(s). For each process \textit{i}, the matrix information is written in ``\texttt{filename-i}". If \textit{file$\_$name} is \textit{NULL}, \texttt{msi$\_$matrix$\_$print} is performed.
PUMI provides an equivalent API for fields and nodes.
